Enhancement of SDR in Thessaloniki

### 2024-04-22 GHI_enh_04_investigate.tex
Commit 2024-04-22 06:14

lmD: 1.552161 +/- 0.104876

lmY: 1.552176 +/- 0.104878

Arima: 1.552549 +/- 0.14034

@@

lmD: 0.954836 +/- 0.154734

lmY: 0.954859 +/- 0.154736

Arima: 1.024507 +/- 0.23503

@@

lmD: 1.088987 +/- 0.16743

lmY: 1.089013 +/- 0.167433

Arima: 1.160151 +/- 0.24838

@@

lmD: 1.050842 +/- 0.240164

lmY: 1.050851 +/- 0.240168

Arima: 1.050895 +/- 0.364666

@@

lmD: 0.958299 +/- 0.253655

lmY: 0.958309 +/- 0.25366

Arima: 0.958355 +/- 0.388216

@@

lmD: 1.089066 +/- 0.07424

lmY: 1.089079 +/- 0.074241

Arima: 1.089082 +/- 0.109498

@@

lmD: 1.136243 +/- 0.070602

lmY: 1.136256 +/- 0.070603

Arima: 1.136263 +/- 0.100583

@@

lmD: 33.75698 +/- 5.702807

lmY: 33.75752 +/- 5.702906

Arima: 33.816428 +/- 8.918367

@@

lmD: 0.003302 +/- 0.00027

lmY: 0.003302 +/- 0.00027

Arima: 0.003326 +/- 0.000357

@@

lmD: 0.001743 +/- 0.000278

lmY: 0.001743 +/- 0.000278

Arima: 0.001906 +/- 0.000459

@@

lmD: 0.001718 +/- 0.000312

lmY: 0.001718 +/- 0.000312

Arima: 0.001883 +/- 0.000503

@@

lmD: 0.001896 +/- 0.000307

lmY: 0.001896 +/- 0.000307

Arima: 0.001896 +/- 0.000479

@@

lmD: 0.001823 +/- 0.000299

lmY: 0.001823 +/- 0.000299

Arima: 0.001823 +/- 0.00046

@@

lmD: 0.002414 +/- 0.000233

lmY: 0.002414 +/- 0.000233

Arima: 0.002414 +/- 0.000362

@@

lmD: 0.002624 +/- 0.000228

lmY: 0.002624 +/- 0.000228

Arima: 0.002624 +/- 0.000339

@@

lmD: 0.988112 +/- 0.144355

lmY: 0.988134 +/- 0.144358

Arima: 1.051184 +/- 0.218585

@@

lmD: 0.816129 +/- 0.101923

lmY: 0.816139 +/- 0.101925

Arima: 0.816132 +/- 0.119665

@@

lmD: 0.215792 +/- 0.037414

lmY: 0.215795 +/- 0.037415

Arima: 0.215796 +/- 0.040986

@@

lmD: 0.181869 +/- 0.03711

lmY: 0.181874 +/- 0.037111

Arima: 0.181874 +/- 0.039209

@@

lmD: 0.481659 +/- 0.045723

lmY: 0.481664 +/- 0.045724

Arima: 0.481665 +/- 0.054201

@@

lmD: 0.001364 +/- 0.01878

lmY: 0.001365 +/- 0.018781

Arima: 0.001365 +/- 0.01932

@@

lmD: -0.018679 +/- 0.017374

lmY: -0.018679 +/- 0.017374

Arima: -0.018679 +/- 0.017837

@@

lmD: 0.496018 +/- 0.071855

lmY: 0.496024 +/- 0.071857

Arima: 0.496022 +/- 0.080622

@@

lmD: 0.597354 +/- 0.08202

lmY: 0.597361 +/- 0.082022

Arima: 0.597357 +/- 0.094227

@@

lmD: 1.432631 +/- 0.148944

lmY: 1.432652 +/- 0.148947

Arima: 1.432652 +/- 0.180994

@@

lmD: 0.001383 +/- 0.000137

lmY: 0.001383 +/- 0.000137

Arima: 0.001383 +/- 0.00016

@@

lmD: 0.00044 +/- 6.1e-05

lmY: 0.00044 +/- 6.1e-05

Arima: 0.00044 +/- 7e-05

@@

lmD: 0.000363 +/- 6.4e-05

lmY: 0.000363 +/- 6.4e-05

Arima: 0.000363 +/- 7.2e-05

@@

lmD: 4e-05 +/- 3.3e-05

lmY: 4e-05 +/- 3.3e-05

Arima: 4e-05 +/- 3.8e-05

@@

lmD: 5e-06 +/- 2.9e-05

lmY: 5e-06 +/- 2.9e-05

Arima: 5e-06 +/- 3.4e-05

@@

lmD: 0.000968 +/- 0.000108

lmY: 0.000968 +/- 0.000108

Arima: 0.000968 +/- 0.000125

@@

lmD: 0.001126 +/- 0.000119

lmY: 0.001126 +/- 0.000119

Arima: 0.001126 +/- 0.000138

@@

lmD: 0.036713 +/- 0.003659

lmY: 0.036714 +/- 0.003659

Arima: 0.036714 +/- 0.00425

@@

lmD: 0.203753 +/- 0.246152

lmY: 0.20379 +/- 0.246156

Arima: 0.191314 +/- 0.355242

@@

lmD: 0.066924 +/- 0.186933

lmY: 0.066947 +/- 0.186936

Arima: 0.031787 +/- 0.332858

@@

lmD: 0.108038 +/- 0.185587

lmY: 0.10806 +/- 0.18559

Arima: 0.07227 +/- 0.320898

@@

lmD: -0.047504 +/- 0.172428

lmY: -0.047493 +/- 0.17243

Arima: -0.093727 +/- 0.32618

@@

lmD: -0.06805 +/- 0.171992

lmY: -0.068039 +/- 0.171995

Arima: -0.113836 +/- 0.324815

@@

lmD: 0.1818 +/- 0.225799

lmY: 0.181836 +/- 0.225802

Arima: 0.164846 +/- 0.343081

@@

lmD: 0.192758 +/- 0.234509

lmY: 0.192794 +/- 0.234513

Arima: 0.178049 +/- 0.348128

@@

lmD: 0.372906 +/- 0.252445

lmY: 0.372932 +/- 0.252449

Arima: 0.373033 +/- 0.257109

@@

lmD: 0.000567 +/- 0.000291

lmY: 0.000567 +/- 0.000291

Arima: 0.000567 +/- 0.000322

@@

lmD: 0.000397 +/- 0.000226

lmY: 0.000397 +/- 0.000226

Arima: 0.000393 +/- 0.000269

@@

lmD: 0.000416 +/- 0.000234

lmY: 0.000416 +/- 0.000234

Arima: 0.000413 +/- 0.000274

@@

lmD: 0.000209 +/- 0.000208

lmY: 0.000209 +/- 0.000208

Arima: 0.000203 +/- 0.000261

@@

lmD: 0.000194 +/- 0.000208

lmY: 0.000194 +/- 0.000208

Arima: 0.000187 +/- 0.000261

@@

lmD: 0.000565 +/- 0.000272

lmY: 0.000565 +/- 0.000272

Arima: 0.000565 +/- 0.000304

@@

lmD: 0.000571 +/- 0.00028

lmY: 0.000571 +/- 0.00028

Arima: 0.000571 +/- 0.000312

@@

lmD: 0.008989 +/- 0.005522

lmY: 0.008989 +/- 0.005522

Arima: 0.009015 +/- 0.00575

@@

Arima: 0.215796 +/- 0.040986

@@

\begin{verbatim}
Warning: Removed 25 rows containing missing values or values outside the scale
range (`geom_bar()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 16 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 16 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 1 row containing missing values or values outside the scale
range (`geom_tile()`).
\end{verbatim}

@@

lmY: 339.1753 +/- 35.87673

@@

lmY: 123.4768 +/- 11.47021

@@

lmY: 0.228163 +/- 0.054288

@@

lmY: 0.174806 +/- 0.039192

@@

\begin{verbatim}
2024-04-19 10:28:33.6 athan@sagan GHI_enh_04_investigate.R 0.788870 mins
\end{verbatim}

>>>>

lmD: 1.534136 +/- 0.10269

lmY: 1.534151 +/- 0.102692

Arima: 1.534524 +/- 0.137014

@@

lmD: 0.957882 +/- 0.154677

lmY: 0.957905 +/- 0.15468

Arima: 1.026834 +/- 0.234823

@@

lmD: 1.097965 +/- 0.167082

lmY: 1.097991 +/- 0.167085

Arima: 1.168104 +/- 0.247425

@@

lmD: 1.054627 +/- 0.240574

lmY: 1.054636 +/- 0.240578

Arima: 1.054681 +/- 0.36529

@@

lmD: 0.96011 +/- 0.254278

lmY: 0.96012 +/- 0.254282

Arima: 0.960167 +/- 0.389374

@@

lmD: 1.084083 +/- 0.073658

lmY: 1.084096 +/- 0.073659

Arima: 1.0841 +/- 0.108761

@@

lmD: 1.123441 +/- 0.069672

lmY: 1.123454 +/- 0.069673

Arima: 1.123462 +/- 0.099367

@@

lmD: 33.98221 +/- 5.725078

lmY: 33.98275 +/- 5.725178

Arima: 34.039551 +/- 9.00373

@@

lmD: 0.003272 +/- 0.000268

lmY: 0.003272 +/- 0.000268

Arima: 0.003296 +/- 0.000354

@@

lmD: 0.001727 +/- 0.000275

lmY: 0.001727 +/- 0.000275

Arima: 0.001888 +/- 0.000454

@@

lmD: 0.001702 +/- 0.000309

lmY: 0.001702 +/- 0.000309

Arima: 0.001865 +/- 0.000498

@@

lmD: 0.001878 +/- 0.000305

lmY: 0.001878 +/- 0.000305

Arima: 0.001878 +/- 0.000475

@@

lmD: 0.001807 +/- 0.000297

lmY: 0.001807 +/- 0.000297

Arima: 0.001807 +/- 0.000456

@@

lmD: 0.002392 +/- 0.000231

lmY: 0.002392 +/- 0.000231

Arima: 0.002392 +/- 0.000359

@@

lmD: 0.0026 +/- 0.000226

lmY: 0.0026 +/- 0.000226

Arima: 0.0026 +/- 0.000336

@@

lmD: 0.982152 +/- 0.142979

lmY: 0.982174 +/- 0.142982

Arima: 1.043911 +/- 0.216442

@@

lmD: 0.76413 +/- 0.10147

lmY: 0.764141 +/- 0.101472

Arima: 0.764136 +/- 0.117502

@@

lmD: 0.202029 +/- 0.037949

lmY: 0.202033 +/- 0.03795

Arima: 0.202033 +/- 0.041317

@@

lmD: 0.164435 +/- 0.03794

lmY: 0.164439 +/- 0.037941

Arima: 0.164439 +/- 0.040154

@@

lmD: 0.430568 +/- 0.042844

lmY: 0.430573 +/- 0.042845

Arima: 0.430575 +/- 0.050183

@@

lmD: -0.009715 +/- 0.019808

lmY: -0.009713 +/- 0.019809

Arima: -0.009713 +/- 0.019969

@@

lmD: -0.024545 +/- 0.018498

lmY: -0.024544 +/- 0.018499

Arima: -0.024544 +/- 0.018581

@@

lmD: 0.467007 +/- 0.072175

lmY: 0.467013 +/- 0.072176

Arima: 0.467011 +/- 0.080184

@@

lmD: 0.567078 +/- 0.082222

lmY: 0.567087 +/- 0.082223

Arima: 0.567084 +/- 0.093419

@@

lmD: 1.246547 +/- 0.136785

lmY: 1.246567 +/- 0.136788

Arima: 1.246568 +/- 0.164233

@@

lmD: 0.001291 +/- 0.000137

lmY: 0.001291 +/- 0.000137

Arima: 0.001291 +/- 0.000158

@@

lmD: 0.000409 +/- 6.1e-05

lmY: 0.000409 +/- 6.1e-05

Arima: 0.000409 +/- 7e-05

@@

lmD: 0.00033 +/- 6.4e-05

lmY: 0.00033 +/- 6.4e-05

Arima: 0.00033 +/- 7.2e-05

@@

lmD: 1.8e-05 +/- 3.3e-05

lmY: 1.8e-05 +/- 3.3e-05

Arima: 1.8e-05 +/- 3.8e-05

@@

lmD: -8e-06 +/- 3e-05

lmY: -8e-06 +/- 3e-05

Arima: -8e-06 +/- 3.5e-05

@@

lmD: 0.00091 +/- 0.000108

lmY: 0.00091 +/- 0.000108

Arima: 0.00091 +/- 0.000124

@@

lmD: 0.001059 +/- 0.000118

lmY: 0.001059 +/- 0.000118

Arima: 0.001059 +/- 0.000137

@@

lmD: 0.031908 +/- 0.003379

lmY: 0.031908 +/- 0.003379

Arima: 0.031908 +/- 0.003889

@@

lmD: 0.210914 +/- 0.239629

lmY: 0.21095 +/- 0.239633

Arima: 0.199623 +/- 0.33989

@@

lmD: 0.075139 +/- 0.179414

lmY: 0.075162 +/- 0.179417

Arima: 0.041751 +/- 0.315453

@@

lmD: 0.116601 +/- 0.178114

lmY: 0.116622 +/- 0.178117

Arima: 0.082858 +/- 0.303922

@@

lmD: -0.039715 +/- 0.164546

lmY: -0.039705 +/- 0.164548

Arima: -0.084179 +/- 0.309433

@@

lmD: -0.059533 +/- 0.164108

lmY: -0.059523 +/- 0.164111

Arima: -0.103637 +/- 0.308351

@@

lmD: 0.190061 +/- 0.219003

lmY: 0.190097 +/- 0.219007

Arima: 0.174594 +/- 0.326917

@@

lmD: 0.200402 +/- 0.22785

lmY: 0.200437 +/- 0.227854

Arima: 0.187023 +/- 0.332301

@@

lmD: 0.360189 +/- 0.242668

lmY: 0.360214 +/- 0.242672

Arima: 0.36031 +/- 0.247054

@@

lmD: 0.000562 +/- 0.000289

lmY: 0.000562 +/- 0.000289

Arima: 0.000562 +/- 0.000319

@@

lmD: 0.000393 +/- 0.000224

lmY: 0.000393 +/- 0.000224

Arima: 0.00039 +/- 0.000267

@@

lmD: 0.000413 +/- 0.000232

lmY: 0.000413 +/- 0.000232

Arima: 0.000409 +/- 0.000272

@@

lmD: 0.000208 +/- 0.000207

lmY: 0.000208 +/- 0.000207

Arima: 0.000201 +/- 0.000259

@@

lmD: 0.000192 +/- 0.000206

lmY: 0.000192 +/- 0.000206

Arima: 0.000185 +/- 0.000259

@@

lmD: 0.00056 +/- 0.000269

lmY: 0.00056 +/- 0.000269

Arima: 0.00056 +/- 0.000301

@@

lmD: 0.000566 +/- 0.000278

lmY: 0.000566 +/- 0.000278

Arima: 0.000566 +/- 0.000309

@@

lmD: 0.008619 +/- 0.005275

lmY: 0.00862 +/- 0.005275

Arima: 0.008644 +/- 0.005494

@@

Arima: 0.202033 +/- 0.041317

@@

\begin{verbatim}
Warning: Removed 26 rows containing missing values or values outside the scale
range (`geom_bar()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 13 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 13 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 2 rows containing missing values or values outside the scale
range (`geom_tile()`).
\end{verbatim}

@@

lmY: 293.3335 +/- 31.54861

@@

lmY: 110.0865 +/- 10.13369

@@

lmY: 0.220182 +/- 0.057217

@@

lmY: 0.168073 +/- 0.041495

@@

\begin{verbatim}
2024-04-21 18:52:46.0 athan@tyler GHI_enh_04_investigate.R 1.292554 mins
\end{verbatim}
